---
title: "Assignment B-1"
author: "Armaghan Sarvar"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading the the Necessary Packages

```{r}
library(datateachr)  # provides 7 semi-tidy datasets
library(tidyverse)  # provides data analysis libraries
library(testthat)
```

# Exercise 1 and 2: Make a Function and Document it

* making a function, fortifying and documenting it. *

The implemented function computes the range, mean, standard deviation and median of a variable across the groups of another variable from the input dataset.
I have also edited the implemented function so that it includes conditions that check the input arguments. More specifically, I first check the type of the first argument which has to be of the dataframe class, and considering the fact that the `feature` input is not limited to any criteria here, I also check whether the `variable` input is numeric. Finally, I check whether the length of the `feature` and `variable` vectors is not zero. 

```{r}
#' Using roxygen to document the function defined 
#' @title Statistical Measurements for a Dataset Variable
#' @description Computing the range, mean, median, and standard deviation of a variable across the groups of a feature from a dataset.
#' @param dataset: The Tibble or Dataframe that the function will look at in order to extract the above information
#' @param feature: The dataset column that we want to group the categories for
#' @param variable: The dataset column that we want to calculate statistics on
#' @return A tibble, showing the statistics calculated

my_function <- function(dataset, feature, variable) {
    if(!is.data.frame(dataset)) {
      stop('Your first argument should be of type dataframe. However, your input dataset is of class:', class(dataset))
    }
   calculations <- dplyr::summarise(
    dataset,
    is_numeric_variable = is.numeric({{ variable }}),
    class_variable = class({{ variable }}),
    length_variable = length({{variable}}),
    length_feature = length({{feature}})
  )
  if (!calculations$is_numeric_variable) {
    stop("`variable` column must be numeric, but it is an object of class ",
         calculations$class_variable)
  }
  if(calculations$length_variable == 0 | calculations$length_feature == 0){
    stop('One of the variable or feature input arguments is of length zero!')
  }
  output <- (dataset %>%
  group_by({{feature}}) %>%
  summarize(range({{variable}})[1], range({{variable}})[2], mean({{variable}}), median({{variable}}), sd({{variable}})))
  return(output)
}

```


# Exercise 3: Include examples
Here, we will demonstrate the usage of the implemented function with a few examples. 

* Example 1

```{r}
cancer_sample
```

First, I will rewrite what the function does in the below code chunk separately to have a performance baseline.

```{r}
cancer_sample_summary <- cancer_sample %>% 
              group_by(diagnosis) %>%
              summarize(range(area_mean)[1], range(area_mean)[2], mean(area_mean), median(area_mean), sd(area_mean))
print(cancer_sample_summary)

```

Here, I will call the function with the same input arguments as the baseline chunk above for comparison.

```{r}
my_function(cancer_sample, diagnosis, area_mean)
```
As we can see, the output is the same, so we have successfully put the functionality we want in the `my_function` function, and we do not have to rewrite the code inside our function for every different possible `dataset`, `feature` and `variable` value. 

* Providing examples for other sample function inputs: *

* Example 2

```{r}
vancouver_trees
```

Testing the function when we want to have the summary statistics of the `diameter` variable considering the categories of the `genus_name` feature. 

```{r}
my_function(vancouver_trees, genus_name, diameter)
```

* Example 3

Now, let's deliberately show an error which can happen due to the `variable` column being non-numeric.

```{r error = TRUE}
my_function(vancouver_trees, genus_name, std_street)
```

* Example 4

```{r}
flow_sample
```

Testing the function when we want to have the summary statistics of the `flow` variable considering different values of the `year` feature. 

```{r}
my_function(flow_sample, year, flow)
```


# Exercise 4: Test the Function

Here, we aim to write a formal testing for the implemented function. I test the conditions that have been implemented in the functions regarding the criteria each input argument should follow.

```{r}
function_testing <- test_that("Testing the implemented function", {
  expect_error(my_function('cancer_sample', diagnosis, area_mean))
  expect_error(my_function(vancouver_trees, genus_name, std_street))
  expect_error(my_function(cancer_sample, diagnosis, numeric(0)))
  expect_error(my_function(cancer_sample, numeric(0), area_mean))
  expect_true(is.data.frame(cancer_sample))
  expect_true(is.numeric(cancer_sample$area_mean))
})
```




