---
title: "STAT545B Assignment B2"
author: "Armaghan Sarvar"
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Package Description

**Package name:** Stat545ArmaghanSarvar

**Package latest version:** 0.1.0

The `Stat545ArmaghanSarvar` package is made by Armaghan Sarvar for the STAT545B course at the University of British Columbia.
The main goal of this package is to make data analysis more efficient for different R users. 
This package provides a function named `my_function` that computes summary statistics range, mean, standard
deviation and median of a variable across the groups of another variable from an input dataset in the datateachr package.


## Installation Instructions

The released development version of the `Stat545ArmaghanSarvar` package can be
installed by running:

``` r
# install.packages("devtools")
devtools::install_github("https://github.com/ArmaghanSarvar/STAT545B-Assignments/tree/main/Stat545ArmaghanSarvar")
``` 

Then, you can load the package with:

``` r
library("Stat545ArmaghanSarvar")
```

Note that once the package is submitted to CRAN, the final released version with the final installation instructions will become available.

## Usage Example

In the following, you can find some examples on the demonstrated usage of the provided package.

```{r}
library(Stat545ArmaghanSarvar)
#' @example
#' # An example of the function ran in Flow_Samples data set
#my_function(datateachr::flow_sample,month,flow)
#' @example
#' # An example of the function ran in Vancouver_Trees data set
# my_function(datateachr::cancer_sample, diagnosis, area_mean)
#' @example
#' # An example of the function ran in Cancer_Sample data set
#my_function(datateachr::cancer_sample,diagnosis,radius_mean)
```


